Design, Implementation, and Evaluation of Open Power Quality

### 2020-07-16 cover-letter/reviewer-3.tex
checkpoint

Thanks for the kind words.

@@

Fixed.  The issue is incorporating modern web application development as the target domain.  The tech stack associated with modern web application development is complex enough that the semester can easily devolve into ``learning the tech stack", not ``experience software engineering".  Historically, the target domains for project, studio, and flipped pedagogies required only a simple tech stack and so this was not an issue.

>>>>

Thanks for the kind words. As part of the paper reorganization and shortening, Figure 6 has been removed.

@@

Thanks again!  The rewrite attempts to inject more scientific background.
